---
title: "Shooting Environment Service Request Performance"
subtitle: ""
author: <a href=mailto:justin.elszasz@baltimorecity.gov>justin.elszasz@baltimorecity.gov</a>
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    code_folding: hide
    fig_height: 4
    fig_width: 6
    toc: yes
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: inline
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@300&display=swap');
</style>

```{css, echo=FALSE}
* {
  font-family: 'Roboto', sans-serif;
}

h1, .h1  {
    margin-top: 70px;
}
```

<img src=`r "https://images.squarespace-cdn.com/content/5b32397bf79392af6b062048/1578532761811-Y6J7YANV433GI2O8YPXV/OPI_Logo.png?content-type=image%2Fpng"` width="200">

```{r setup, include = FALSE, echo = FALSE, message = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  include = T,
  cache = F,
  fig.width = 6, 
  fig.height = 4,
  out.width = "100%", 
  out.height = "100%"
  )

knitr::clean_cache(
  clean = FALSE, 
  path = knitr::opts_chunk$get("cache.path")
  )
```

```{r load_packages}
library(tidyverse)
library(lubridate)
library(sf)
library(leaflet)
library(ggiteam)
library(kableExtra)
library(htmltools)
library(DT)
library(RSocrata)
```


```{r}
report_list <- list.files("reports/sent/", pattern = "*.csv")
```

```{r}
for (report in report_list){
  
  report_temp <- read_csv(paste0("reports/sent/", report))
  report_temp$reportdate <- as.POSIXct(substr(report, nchar(report) - 13, nchar(report) - 4))
  
  if (report == report_list[1]){
    all_reports <- report_temp
  } else {
    # should add a field for the report date
    all_reports <- bind_rows(all_reports, report_temp)
  }
}
```

```{r}
sr_filtered <- sr %>%
  filter(servicerequestnum %in% unique(all_reports$servicerequestnum)) %>%
  left_join(all_reports %>% select(servicerequestnum, reportdate), by = c("servicerequestnum"))
```

#  Overall Percent Remaining Open From Previous Reports: `r ((sr_filtered %>% filter(srstatus %in% c("Open", "New")) %>% nrow) / nrow(sr_filtered)) %>% scales::percent()`

# Number of Total Service Requests Remaining Open

```{r}
sr_filtered %>%
  filter(srstatus %in% c("Open", "New")) %>%
  count(srtype)  %>%
  arrange(desc(n))
```

# Number of Service Requests Originally in Each Report

```{r, fig.width = 6, fig.height = 2, out.width = "100%"}
all_reports %>% 
  count(reportdate) %>%
  ggplot(aes(reportdate, n)) +
  geom_col() +
  geom_text(aes(reportdate, n + 20, label = n)) +
  geom_text(aes(reportdate, 50, label = format(reportdate, "%m/%d")), color = "white") +
  scale_x_datetime(breaks = "1 month", date_labels = format("%B\n%Y"))  +
  theme_iteam_presentations() +
  labs(x = "Date Report Sent") +
  theme(axis.title.y = element_blank()) 
  
```

  

# On-time Performance for Closed SRs: `r ontime_pct <- sr_filtered %>% mutate(ontime = ifelse(statusdate <= duedate, T, F)) %>% filter(srstatus == "Closed") %>% count(ontime) %>% mutate(pct = round(100* n / sum(n)), 0) %>% filter(ontime == T) %>% select(pct) %>% pull(); paste0(ontime_pct, "%")`


```{r fig.width = 6, fig.height = 2}
# reports_all_duedates_passed <- sr_filtered %>%
#   group_by(reportdate) %>%
#   summarise(last_duedate = max(duedate)) %>%
#   filter(last_duedate < today()) %>%
#   select(reportdate) %>%
#   pull()
# 
# sr_filtered %>%
#   filter(reportdate %in% reports_all_duedates_passed) %>%
#   filter(duedate < today()) %>%
#   count(agency, reportdate, closedate <= duedate) %>%
#   group_by(agency, reportdate) %>%
#   mutate(pct = n / sum(n)) %>%
#   filter(`closedate <= duedate` == TRUE) %>%
#   ggplot(aes(reportdate, pct, color = agency)) +
#   geom_line() +
#   geom_point() +
#   theme_iteam_google_docs() +
#   scale_y_continuous(limits = c(0,1), labels = scales::percent) +
#     #scale_x_datetime(breaks = "1 month", date_labels = format("%B\n%Y"))  +
#   theme_iteam_google_docs() +
#   labs(title = "On-Time Performance for Past Reports",
#        x = "Date Report Sent") +
#   theme(axis.title.y = element_blank()) 
#   
```

```{r fig.width = 4, fig.height = 2, out.width="100%"}
reports_all_duedates_passed <- sr_filtered %>%
  group_by(reportdate) %>%
  summarise(last_duedate = max(duedate)) %>%
  filter(last_duedate < today()) %>%
  select(reportdate) %>%
  pull()

sr_filtered %>%
  filter(reportdate %in% reports_all_duedates_passed) %>%
  filter(duedate < today()) %>%
  count(srtype, reportdate, closedate <= duedate) %>%
  group_by(srtype, reportdate) %>%
  mutate(pct = n / sum(n)) %>%
  filter(`closedate <= duedate` == TRUE) %>%
  ggplot(aes(reportdate, pct, color = srtype)) +
  geom_line() +
  geom_point() +
  facet_wrap(~srtype) +
  theme_iteam_presentations() +
  scale_y_continuous(limits = c(0,1), labels = scales::percent) +
    #scale_x_datetime(breaks = "1 month", date_labels = format("%B\n%Y"))  +
  theme_iteam_google_docs() +
  labs( x = "Date Report Sent",
       y = "Percent SRs Completed On-Time")
  
```




# Percent of SRs Closed Within Timeframe 

```{r fig.width = 8, fig.height = 6, out.width="100%"}
levels <- c(
  "Within 7 Days",
  "Within 14 Days",
  "Within 30 Days",
  "More Than 30 Days"
)


close_windows <- sr_filtered %>%
  mutate(close_window = case_when(
    closedate <= (reportdate + days(7)) ~ "Within 7 Days", 
    closedate <= (reportdate + days(14)) ~ "Within 14 Days", 
    closedate <= (reportdate + days(30)) ~ "Within 30 Days",
    TRUE ~ "More Than 30 Days"),
    close_window = factor(close_window, levels = levels)) %>%
  count(reportdate, srtype, close_window) %>%
  group_by(reportdate, srtype) %>%
  arrange(close_window) %>%
  mutate(pct = n / sum(n),
         cumsum = cumsum(n),
         cumpct = cumsum / sum(n)) %>%
  filter(!(close_window == "More Than 30 Days")) %>%
  ungroup() 


close_windows %>%
  mutate(reportdate = as.factor(reportdate)) %>%
  ggplot(aes(x = close_window, y = cumpct, group = reportdate, color = reportdate)) +
  geom_line(size = 1) +
  geom_point(size = 1) +
  facet_wrap(~srtype) +
  ylim(c(0, 1)) +
  theme_iteam_presentations() +
  scale_color_brewer() +
  scale_y_continuous(
    name = "Percent Service Requests Completed Within Timeframe", 
    limits = c(0,1), 
    labels = scales::percent) +
  labs(x = element_blank()) +
  theme(axis.text.x = element_text(angle = 90))
#scale_color_datetime(low = "gray90", high = "gray10")

```

# Rapid City Response to Shooting Sites
Percent of service requests that are closed with 7 days of being opened.

```{r out.width = "100%", fig.width = 8, fig.height = 6}
close_windows %>%
  mutate(reportdate = as.Date(reportdate)) %>%
  filter(close_window == "Within 7 Days",
         reportdate < today() - 7) %>%
  ggplot(aes(reportdate, pct)) +
  geom_line() + 
  geom_point() + 
  geom_text(
    aes(reportdate, pct, 
        label = ifelse(reportdate == max(reportdate), paste0(100 * round(pct, 2), "%\n", n, " SRs"), "")),
    nudge_y = -.1,
    nudge_x = -3,
    hjust = 1) + 
  facet_wrap(~srtype) +
  theme_iteam_presentations() +
  scale_y_continuous(labels = scales::percent)+
  scale_x_date() +
  labs(
    y = "Percent of SR's Closed Within 7 Days",
    x = "Report Date"
  )
```




```{r include=F}
sessionInfo()
```

